Live Functional Programming with Typed Holes

### 2018-04-17 qsort-example.tex
missing files

\begin{figure}[t]
\begin{subfigure}[t]{\textwidth}
\centering
\includegraphics[width=0.85\textwidth,interpolate=false]{images/grades-cell-mockup.png}
\caption{Evaluating an incomplete functional program past the first hole}
\label{fig:grades-cell-mockup}
\end{subfigure}

\vspace{10px}

\begin{subfigure}[t]{\textwidth}
\centering
\includegraphics[width=0.3\textwidth,interpolate=false]{images/grades-sidebar-1.png}
~${}^\blacktriangleright$
\includegraphics[width=0.3\textwidth,interpolate=false]{images/grades-sidebar-2.png}
~${}^\blacktriangleright$
\includegraphics[width=0.3\textwidth,interpolate=false]{images/grades-sidebar-3.png}
\caption{The programming environment communicates relevant static \emph{and} dynamic information in a sidebar.}
\label{fig:grades-sidebar}
\end{subfigure}
% %% TODO once the code above is removed, scale up the screenshots
% \includegraphics[scale=0.20]{images/hazel-placeholder-0.png}

@@

% \includegraphics[scale=0.20]{images/hazel-placeholder-1a.png}
\vspace{5px}

\caption{Example 1: Grades}
\label{fig:grades-example}
\vspace{-8px}
\end{figure}

>>>>

\begin{figure}[t]
% \begin{subfigure}[t]{\textwidth}
\includegraphics[width=0.7\textwidth,interpolate=false,valign=t]{images/qsort-code.png}
\includegraphics[width=0.29\textwidth,interpolate=false,valign=t]{images/qsort-sidebar-1.png}
\caption{Example 2: Incomplete Quicksort}
\label{fig:qsort-cell-mockup}
% \end{subfigure}
\vspace{-6px}
\end{figure}

% \begin{subfigure}[t]{\textwidth}
% \centering
% \includegraphics[width=0.3\textwidth,interpolate=false]{images/grades-sidebar-1.png}
% ~${}^\blacktriangleright$
% \includegraphics[width=0.3\textwidth,interpolate=false]{images/grades-sidebar-2.png}
% ~${}^\blacktriangleright$
% \includegraphics[width=0.3\textwidth,interpolate=false]{images/grades-sidebar-3.png}
% \caption{Typing context view with live hole closure information}
% \label{sec:grades-sidebar}
% \end{subfigure}
% %% TODO once the code above is removed, scale up the screenshots
% \includegraphics[scale=0.20]{images/hazel-placeholder-0.png}

@@

% \includegraphics[scale=0.20]{images/hazel-placeholder-1a.png}
